Analyzing Coopetition Strategies of Services within Communities

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Chart Changes
Changes

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts web services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a random reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the web service cannot
compete, the procedure would suggest to collaborate, which is
better than competing and failing to obtain the task. In this case
(i.e., competing and not getting the task), the service stays idle
but still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some web services to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to get a task. This kind of
strategy selection is totally stochastic while the task allocation
algorithm follows a logical path. The ideal system is the one that
analyzes the optimal strategic path and consistently follows
strategies that bring maximum outcome. The result regarding the
community that follows the random strategy shows how stochastic
decision making degrades the community budget, but still this
result outperforms the one of the purely competitive community. In
the last case, all the services follow the competitive strategy
and the frequency of getting rejected from a task is relatively
high. In a community with limited number of tasks, the competitive
strategy for all services highly influences the community budget
because a potential group of services are losing at every run.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.6]{graph1Final+.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

@@

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.33]{Graph2.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}

We conclude our analysis by discussing the percentage of correct
strategy selection (Figure \ref{Graph3}). By this we mean the
average of web services that can get a task when the coopetitive
strategy is followed. We observe that in different runs, this
percentage is generally increasing. This shows that over runs the
web services get to learn the threshold $\tau_w^t$ that allows
them to select the good strategy. We should notice that in
different runs different initial values of the threshold are used
ranging from $0.3$ for run 1 to $0.6$ for run 4.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.33]{graph3Final+.eps}
\caption{Percentage of correct strategy selection in different
runs using different initial threshold values.} \label{Graph3}
\end{figure}

>>>>

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts web services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a random reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the web service cannot
compete, the procedure would suggest to collaborate, which is
better than competing and failing to obtain the task. In this case
(i.e., competing and not getting the task), the service stays idle
but still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some web services to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to perform a task with high QoS requirements. This kind of
strategy selection is totally stochastic while the task allocation
algorithm follows a logical path. The ideal system is the one that
analyzes the optimal strategic path and consistently follows
strategies that bring maximum outcome. The result regarding the
community that follows the random strategy shows how stochastic
decision making degrades the community budget, but still this
result outperforms the one of the purely competitive community. In
the last case, all the services follow the competitive strategy
and the frequency of getting rejected from a task is relatively
high. In a community with limited number of tasks, the competitive
strategy for all services highly influences the community budget
because a potential group of services are losing at every run.

\begin{figure}%[h]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.41]{graphbgtmed.eps}
\includegraphics[scale=0.41]{graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.275]{graphbgtmed3set.eps}
\includegraphics[scale=0.275]{graphbgthigh.eps}
\includegraphics[scale=0.275]{graphbgtveryhigh.eps}
\caption{High membership fees or less task income impacts on different selection strategies, (a) medium membership fee, (b) high membership fee, (c) very high membership fee} \label{membership_fee_graph}
\end{figure}

\begin{figure}%[h]
\centering
\includegraphics[scale=0.275]{graphtaskdone.eps}
\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
\includegraphics[scale=0.275]{graphavgqostask.eps}
\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
\end{figure}

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.31]{Graph2.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}
average of web services that can get a task when the coopetitive
strategy is followed. We observe that in different runs, this
percentage is generally increasing. This shows that over runs the
web services get to learn the threshold $\tau_w^t$ that allows
them to select the good strategy. We should notice that in
different runs different initial values of the threshold are used
ranging from $0.3$ for run 1 to $0.6$ for run 4.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.4]{graphdev.eps}
\includegraphics[scale=0.4]{graphdev2.eps}
\caption{Utiliy loss while deviating from cooperating decision process, (a) Overall budget when deviating in 0, 10, 20, 30, 40, 50 percent of decision, (b) Ratio of getting earning utility (budget) when deviating from cooperative strategy in 1 to 10 decisions} \label{graph_dev}
\end{figure}
